---
title: "Class 17"
author: "Sean Westwood"
header-includes:
   - \usepackage{pdfpages}
output:
  pdf_document: default
---
```{r setup, echo=F}
library(knitr)
opts_chunk$set(tidy.opts = list(width.cutoff = 60), tidy = TRUE)
knitr::opts_chunk$set(error = TRUE)
```

# Statistical significance: Confidence intervals

## Calculating Confidence intervals

```{r}
transfer <- read.csv("transfer.csv")
```

Difference in means: t.test()

```{r}
t.test(transfer$literate91[transfer$pop82 <= median(transfer$pop82)],
       transfer$literate91[transfer$pop82 >= median(transfer$pop82)])
```

Regression: confint()

```{r}
model <- lm(literate91~pop82, data = transfer)
confint(model)
```

Proportion: prop.test()

```{r}
transfer$big <- 0
transfer$big[transfer$pop82 >10000] <- 1

transfer$poor <- 1
transfer$poor[transfer$poverty91 <.6] <- 0

tab <- table(transfer$big, transfer$poor)

prop.test(tab,conf.level = 0.95)

```


## Evaluation

1. On a scale ranging between 1 (Too Hard) and 10 (Too Easy), how was today's class: 
2. What was the easiest thing to understand?
3. What was the most difficult thing to understand?
4. How long did you spend on the assignment outside of class?